A Catalogue of Twists of Supersymmetric Gauge Theories

### 2020-01-23 paper.tex
small
donaldson

Next, we check that the equivalence respects  the gradings and the $\MU(2)$-action. 
Indeed, the equivalence given by Theorem \ref{thm:5dminimaltwist} eliminates fields $A_{1, 0}, \Tilde{a}, \rho, \chi, \Tilde{\chi}$ and hence the underlying local $L_\infty$ algebra after the twist becomes
\[
\xymatrix@R=0.5cm@C=0.5cm{
\ul{0} & \ul{1} & \ul{2} & \ul{3} & \\ 
\Omega^0(\CC^2; \gg)_c \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{B} \\
 & \Omega^0(\CC^2; \gg)_a \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{b} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{\xi^*} \\
& \Omega^0(\CC^2 ; U)_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U)_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U)_{\varphi^*} \\
\Omega^{2,0}(\CC^2 ; U)_{\varphi} \ar[r] & \Omega^{2,1}(\CC^2 ; U)_{\psi^*} \ar[r] & \Omega^{2,2}(\CC^2 ; U)_{\phi^*} \\
 & \Omega^{2,0}(\CC^2 ; \gg)_{B^*} \ar[r] & \Omega^{2,1}(\CC^2 ; \gg)_{A_{0,1}^*} \ar[r] & \Omega^{2,2}(\CC^2 ; \gg)_{c^*} \\
 \Omega^{2,0}(\CC^2; \gg)_\xi \ar[r] &\Omega^{2,1}(\CC^2; \gg)_{b^*} \ar[r] &\Omega^{2,2}(\CC^2; \gg)_{a^*} 
}
\]
concentrated in cohomological degrees $0, \dots, 3$. These fields have the same degrees as in the holomorphic BF theory and the $L_\infty$ structure is obtained by the natural square zero extension of the dg Lie algebra in the first line by the remaining part of the diagram.
Finally, we observe that the twisted theory manifestly descends to a $\U(2)$-equivariant theory along the natural homomorphism $\MU(2) \to \U(2)$, and all identifications are $\U(2)$-equivariant. 
\end{proof}

@@

Let $V_\RR = \RR^4$ and $V=V_\RR\otimes_\RR\CC$. 
Fix a K\"ahler structure on $\RR^4$ and denote by $L\subset V$ the $i$-eigenspace of the complex structure. %Moreover, fix a complex volume form on $L$.

@@

\begin{prop}
Suppose $Q_t$ is the rank $(2,0)$ supercharge as above.
The $\MU(2)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 4d $\cN=2$ super Yang--Mills theory are
\begin{align*}
I_{\rm gauge}^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(b, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}a, b^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2} \xi^*\wedge B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t a c^*\right).
\end{align*}
\end{prop}
\begin{proof}
We first write down the fields and the functionals in $\Spin(4)$-notation.
Let $S^{2n}_\pm$ be the semi-spin representations of $\Spin(2n , \CC)$.
The decomposition of $S^{6}_+$ under the subgroup $\Spin(4 , \CC) \times \Spin(2, \CC) \subset \Spin(6,\CC)$ is
\[
S_+^6 = S_+^4 \otimes S_+^2 \oplus S_-^4 \otimes S_-^2 .
\]
The odd part of the $\cN=2$ supersymmetry algebra is 
\[
\Sigma = S_+^6 \otimes W_+ \cong S_+^4 \otimes W \oplus S_-^4 \otimes W^* .
\]
where $W_+$ is a complex two-dimensional symplectic vector space. 
From this, we have identifications $W = W_+ \otimes S_+^2$ and $W^* = W_+ \otimes S_-^2$. 
Let $\{u \otimes \alpha_+, v \otimes \alpha_+\}$ be a basis for $W = W_+ \otimes S_+^2$ where $\{u,v\}$ is a symplectic basis for $W_+$ and $s_+$ is a basis element for $S_+^2$. 
A general supercharge $Q \in S_+^4 \otimes W$ is of the form
\[
Q = s_+ \otimes u \otimes \alpha_+ + s_+' \otimes v \otimes \alpha_+ 
\]
where $s_+, s_+' \in S_+^{4d}$.

The fields of $4d \cN=2$ decompose as:
\begin{itemize}
 \item $\gg$-valued Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and a pair of scalar fields $(a \otimes \alpha_-^{\otimes 2} ,\Tilde{a} \otimes \alpha_+^{\otimes 2}) \in \Omega^0(\RR^4; (S^2_-)^{\otimes 2} \gg \oplus  (S^2_-)^{\otimes 2} \otimes \gg)$.
 \item $U$-valued bosons: a $W$-valued scalar field $\phi \otimes v \in \Omega^0(\RR^4; W \otimes U)$.
 \item $\gg$-valued fermions: a $W$-valued Dirac spinor $\lambda = (\lambda_+ \otimes \alpha_+, \lambda_-\otimes \alpha_-) \in \Omega^0(\RR^4; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
 \item $U$-valued fermions: a Dirac spinor $\psi = (\psi_+,\psi_-) \in \Omega^0(\RR^4; (S_+\oplus S_-) \otimes U)$.
 \item a ghost $c \in \Omega^0(\RR^4 ; \gg)$.
\end{itemize}

\brian{If we split $V^{6d}$ as $V^{4d} \oplus N \oplus N^*$ where $N, N^*$ are trivial one-dimensional $\Spin(4)$-representations, then $W^{4d} = W_+^{6d} \otimes N$ and $W^{4d*} = W_+^{6d} \otimes N^*$. 
Moreover, the isomorphism $\wedge^2 S_+^{6d} \cong V^{6d}$ gives rise to three maps
\begin{itemize}
\item $S^{4d}_+ \otimes S^{4d}_- \otimes N \otimes N^* \to V^{4d}$. This is $\Gamma^{4d} \otimes {\rm ev}_N$. 
\item $\wedge^2(S_+^{4d} \otimes N) \to N^*$. 
\item $\wedge^2(S_-^{4d} \otimes N^*) \to N$. 
\end{itemize}
The bosons in the gauge part live in $a \in N^*$ and $\Tilde{a} \in N$. 
For $Q_+ \in S^{4d}_+ \otimes W^{4d} = S^{4d}_+ \otimes W^{6d}_+ \otimes N$ and $\lambda_+ \in S^{4d}_+ \otimes W^{4d} = S^{4d}_+ \otimes W^{6d}_+ \otimes N$. 
I want to make sense of $(\<Q_+, \lambda_+\> , \Tilde{a}^*)$ as a scalar via the composition
\[
\wedge^2 (S_+^{4d} \otimes W^{6d}_+ \otimes N) \otimes N  \xto{\omega_{W_+}} \wedge^2(S^{4d}_+ \otimes N) \otimes N \to N^* \otimes N \to \CC .
\]
The first map is the symplectic pairing on $W_+$. 
The second map is the second bullet above. 
The last map is evaluation.
Do you see an easier way to canonically write this using only 4d objects?
}

For a general supercharge $Q_+ \otimes \alpha_+ \in S_+^4 \otimes W = S^4_+ \otimes W_+ \otimes S_+^2$, the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ decompose as:
\begin{align*}
I^{(1)}_{\mr{gauge}}(Q_+ \otimes \alpha_+) &= \int \dvol \bigg(-( \Gamma(Q_+,\lambda_-), A^*) + (\langle Q_+,\lambda_+\rangle , \Tilde{a}^* ) + \\
&\qquad  + \frac 12 ((\rho(F_A)Q_+, \lambda_+^*)(u_+^*,  w_+) + (\rho(\d_A \phi_2(w_+ \wedge u_-^*))Q_+, \lambda_-^*) \bigg)\\
I^{(1)}_{\mr{matter}}(Q) &= \int \dvol (((Q_+,\psi_+), \phi^*)(v^*,w_+) + \frac 12 (\rho(\d_A \phi)Q_+, \psi_+^*)(v,w_+)) \\
I^{(2)}_{\mr{gauge}}(Q,Q) &= \int \dvol \big(\frac 14 (Q_+,Q_+)(\lambda_-,\lambda_-)(u_-,w_+)^2 - \frac 12  (Q_+, \lambda_-^*)^2(w_+ \wedge u_-^*)^2 - (Q_+,Q_+)\phi_1(w_+ \wedge w_+)c^* \big) \\
I^{(2)}_{\mr{matter}}(Q,Q) &= \int \frac 14 \dvol (Q_+,Q_+)(\psi_-^*,\psi_-^*)(w_-^* \wedge w_-^*)
\end{align*}
if $Q=Q_+ \otimes w_+$ is a non-zero element of $S_+ \otimes W$. \chris{missing thing here: trivialising those wedge pairs, or equivalently restricting $\Gamma(-,-)$ from 6d to 4d.}

>>>>

Next, we check that the equivalence respects  the gradings and the $\MU(2)$-action. 
Indeed, the equivalence given by Theorem \ref{thm:5dminimaltwist} eliminates fields $A_{1, 0}, \Tilde{a}, \rho, \chi, \Tilde{\chi}$ and hence the underlying local $L_\infty$ algebra after the twist becomes
\[
\xymatrix@R=0.5cm@C=0.5cm{
\ul{0} & \ul{1} & \ul{2} & \ul{3} & \\ 
\Omega^0(\CC^2; \gg)_c \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{B} \\
 & \Omega^0(\CC^2; \gg)_a \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{b} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{\xi^*} \\
  & \Omega^{2,0}(\CC^2 ; \gg)_{B^*} \ar[r] & \Omega^{2,1}(\CC^2 ; \gg)_{A_{0,1}^*} \ar[r] & \Omega^{2,2}(\CC^2 ; \gg)_{c^*} \\
 \Omega^{2,0}(\CC^2; \gg)_\xi \ar[r] &\Omega^{2,1}(\CC^2; \gg)_{b^*} \ar[r] &\Omega^{2,2}(\CC^2; \gg)_{a^*}  \\
& \Omega^0(\CC^2 ; U)_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U)_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U)_{\varphi^*} \\
\Omega^{2,0}(\CC^2 ; U)_{\varphi} \ar[r] & \Omega^{2,1}(\CC^2 ; U)_{\psi^*} \ar[r] & \Omega^{2,2}(\CC^2 ; U)_{\phi^*}
}
\]
concentrated in cohomological degrees $0, \dots, 3$. These fields have the same degrees as in the holomorphic BF theory and the $L_\infty$ structure is obtained by the natural square zero extension of the dg Lie algebra in the first line by the remaining part of the diagram.
Finally, we observe that the twisted theory manifestly descends to a $\U(2)$-equivariant theory along the natural homomorphism $\MU(2) \to \U(2)$, and all identifications are $\U(2)$-equivariant. 
\end{proof}

@@

Let $V_\RR = \RR^4$ and $V=V_\RR\otimes_\RR\CC$. 
Fix a K\"ahler structure on $\RR^4$ and denote by $L\subset V$ the $i$-eigenspace of the complex structure.
We utilize the same notation for the fields of super Yang-Mills theory as in the previous section. 
\brian{discuss twisting homomorphism}
%Moreover, fix a complex volume form on $L$.

@@

\begin{prop}
Suppose $Q_t$ is the rank $(2,0)$ supercharge as above.
The $\MU(2)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 4d $\cN=2$ super Yang--Mills theory are
\begin{align*}
I_{\rm gauge}^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(b, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}a, b^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2} \xi^*\wedge B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t a c^*\right) \\
I_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left((\Tilde{\nu}, \nu^*) + t (\varphi, \phi^*) + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*) \right) \\
I_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac 14 t (\psi^*, \psi^*)
\end{align*}
\end{prop}
\begin{proof}
We first write down the fields and the functionals in $\Spin(4)$-notation.
Let $S^{2n}_\pm$ be the semi-spin representations of $\Spin(2n , \CC)$.
The decomposition of $S^{6}_+$ under the subgroup $\Spin(4 , \CC) \times \Spin(2, \CC) \subset \Spin(6,\CC)$ is
\[
S_+^6 = S_+^4 \otimes S_+^2 \oplus S_-^4 \otimes S_-^2 .
\]
The odd part of the $\cN=2$ supersymmetry algebra is 
\[
\Sigma = S_+^6 \otimes W_+ \cong S_+^4 \otimes W \oplus S_-^4 \otimes W^* .
\]
where $W_+$ is a complex two-dimensional symplectic vector space. 
From this, we have identifications $W = W_+ \otimes S_+^2$ and $W^* = W_+ \otimes S_-^2$. 
Let $\{u \otimes \alpha_+, v \otimes \alpha_+\}$ be a basis for $W = W_+ \otimes S_+^2$ where $\{u,v\}$ is a symplectic basis for $W_+$ and $s_+$ is a basis element for $S_+^2$. 
A general supercharge $Q \in S_+^4 \otimes W$ is of the form
\[
Q = s_+ \otimes u \otimes \alpha_+ + s_+' \otimes v \otimes \alpha_+ 
\]
where $s_+, s_+' \in S_+^{4}$.

The fields of $4d \cN=2$ decompose as:
\begin{itemize}
 \item $\gg$-valued bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and a pair of scalar fields $(a \otimes \alpha_-^{\otimes 2} ,\Tilde{a} \otimes \alpha_+^{\otimes 2}) \in \Omega^0(\RR^4; (S^2_-)^{\otimes 2} \otimes \gg \oplus  (S^2_-)^{\otimes 2} \otimes \gg)$.
  \item $\gg$-valued fermions: a $W = W_+ \otimes S_+^2$-valued Dirac spinor $\lambda = (\lambda_+ \otimes \alpha_+, \lambda_-\otimes \alpha_-) \in \Omega^0(\RR^4; (S^4_+ \otimes W \oplus S^4_- \otimes W^*) \otimes \gg)$.
 \item $U$-valued bosons: a $W = W_+ \otimes S_+^2$-valued scalar field $\phi \otimes v \in \Omega^0(\RR^4; W_+ \otimes S_+^2 \otimes U)$.
 \item $U$-valued fermions: a Dirac spinor $\psi = (\psi_+ \otimes \alpha_- ,\psi_- \otimes \alpha_+) \in \Omega^0(\RR^4; (S^4_+ \otimes S_-^2 \oplus S^4_- \otimes S_+^2) \otimes U)$.
 \item a ghost $c \in \Omega^0(\RR^4 ; \gg)$.
\end{itemize}
The anti-fields decompose in an analogous way.

For a general supercharge $Q_+ \otimes \alpha_+ \in S_+^4 \otimes W = S^4_+ \otimes W_+ \otimes S_+^2$, the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ decompose as:
\begin{align*}
I^{(1)}_{\mr{gauge}}(Q_+ \otimes \alpha_+) &= \int \dvol \bigg(-( \Gamma(Q_+,\lambda_-), A^*) + (\langle Q_+,\lambda_+\rangle , \Tilde{a}^* ) + \\
&\qquad  + \frac 12 ((\rho(F_A)Q_+, \lambda_+^*) + (\rho(\d_A a)Q_+, \lambda_-^*) \bigg)\\
I^{(1)}_{\mr{matter}}(Q_+ \otimes \alpha_+) &= \int \dvol (((Q_+,\psi_+), \phi^*) + \frac 12 (\rho(\d_A \phi)Q_+, \psi_+^*)) \\
I^{(2)}_{\mr{gauge}}(Q_+ \otimes \alpha_+) &= \int \dvol \big(\frac 14 (Q_+,Q_+)(\lambda_+^*,\lambda_+^*) - \frac 12  (Q_+, \lambda_+^*)^2 - (Q_+,Q_+) a c^* \big) \\
I^{(2)}_{\mr{matter}}(Q_+ \otimes \alpha_+) &= \int \frac 14 \dvol (Q_+,Q_+)(\psi_-^*,\psi_-^*) .
\end{align*}

The result follows from further decomposing the fields under the action of $\MU(2)$. 
\end{proof}

\begin{thm}
The twist of 4d $\cN=2$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the holomorphic Hodge theory $\map(\CC^2, (U//g)_{\mr{Hod}})$. 
Moreover, this equivalence is $\U(2)$-equivariant.
\label{thm:4dDonaldsontwist}
\end{thm}
\begin{proof}
The proof proceeds as in the proof of Theorem \ref{thm:10dholomorphictwist} with slight modifications.

Observe that the quadruple of fields $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ has the same Poisson brackets as the quadruple $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$. Therefore, we may eliminate the fields $\chi^*-t\wt\chi^*, \chi$ using Proposition \ref{prop:integrateoutfield}. We then have trivial BRST doublets $\{\wt\chi + t\chi, \wt a\}$ and $\{\rho, A_{1, 0}\}$ which may be eliminated using Proposition \ref{prop:BRSTdoublet}. We are left with the action
\[S_{BF} + \int\dvol\left(-t(b, A_{0, 1}^*) + t a c^* + \frac{t}{2} \xi^*\wedge B^* + t (\varphi, \phi^*) + \frac t4 (\psi^*, \psi^*) \right),\]
where $S_{BF}$ is the action functional of the holomorphic twist at $t=0$ found in the previous section. 
Since the extra terms are quadratic in the fields, the claim is reduced to a comparison of the underlying local $L_\infty$ algebra of the twisted theory and that of the holomorphic Hodge theory. The former is given by (cf. the proof of Theorem \ref{thm:4dholomorphictwist})
\[
\xymatrix@R=0.5cm@C=0.5cm{
\ul{-1} & \ul{0} & \ul{1} & \ul{2} & \ul{3} & \ul{4} \\ 
& \Omega^0(\CC^2; \gg)_c \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{B} \\
\Omega^0(\CC^2; \gg)_a  \ar@{-->}^{t\id}[ur] \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{b}  \ar@{-->}^{t\id}[ur] \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{\xi^*}  \ar@{-->}^{t\id}[ur] \\
& &  \Omega^{2,0}(\CC^2 ; \gg)_{B^*}  \ar@{-->}^{t\id}[dr] \ar[r] & \Omega^{2,1}(\CC^2 ; \gg)_{A_{0,1}^*} \ar[r]  \ar@{-->}^{t\id}[dr] & \Omega^{2,2}(\CC^2 ; \gg)_{c^*}  \ar@{-->}^{t\id}[dr] \\
& & & \Omega^{2,0}(\CC^2; \gg)_\xi \ar[r] &\Omega^{2,1}(\CC^2; \gg)_{b^*} \ar[r] &\Omega^{2,2}(\CC^2; \gg)_{a^*}  \\
& \Omega^0(\CC^2 ; U)_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U)_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U)_{\varphi^*} \\
\Omega^{2,0}(\CC^2 ; U)_{\varphi} \ar[r]  \ar@{-->}^{t\id}[ur] & \Omega^{2,1}(\CC^2 ; U)_{\psi^*} \ar[r]  \ar@{-->}^{t\id}[ur]  & \Omega^{2,2}(\CC^2 ; U)_{\phi^*}  \ar@{-->}^{t\id}[ur]
}
\]
which is exactly the local $L_\infty$ algebra of the holomorphic Hodge theory.
\end{proof}

\begin{cor}
The rank $(2,0)$ topological twist of 4d $\cN=2$ super Yang--Mills is perturbatively trivial.
\label{cor:4dDonaldsontwist}
\end{cor}
\begin{proof}
The topological twist of 4d $\cN=2$ super Yang--Mills is the twist by $Q_t$ with $t\neq 0$. By Theorem \ref{thm:4dDonaldsontwist} it is equivalent to the $t\neq 0$ specialization of the holomorphic Hodge theory which by Proposition \ref{prop:Hodgetheoryspecialization} is perturbatively trivial.
\end{proof}
